\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images

\title{Resume}
\author{William Deye}
\date{\today}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
            linkcolor = red,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\hypersetup{pdfborder = 0 0 0}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingBoldNotBold}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \text{\small #2} \\
      \textit{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingT}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\textit{\footnotesize{#2}}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#4}\\
    \end{tabular*}
    \vspace{-2.4mm}
}
\newcommand{\resumeSubSubheading}[2]{
 \vspace{-2pt}
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

\begin{center}
    {\Huge \scshape William Deye} \\ \vspace{1pt}
    \small
    \raisebox{-0.1\height}\faPhone\ (240) 579-8400 ~
    \href{mailto:w.jack.deye@gmail.com}{\faEnvelope\ \underline{w.jack.deye@gmail.com}} ~ 
    \faMapMarker \ Los Angeles, CA ~ 
    \faGithub \ \href{https://github.com/jackdeye}{github.com/jackdeye}
    \vspace{-3pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of California, Los Angeles}{Expected June 2026}
      {B.S. in Mathematics of Computation}{GPA: 3.8/4.0}
      
      {\small{\textbf{Relevant Coursework:} Differential Equations, Linear Algebra, Data Structures and Algorithms, Software Construction, Computer Organization, Mathematical Modeling, Probability and Statistics, Number Theory, Combinatorics}}  
      
    {\small{\textbf{Activities:} Upsilon Pi Epsilon, ACM Hack, Bruin Racing: Super Mileage Vehicle, Club Sports: Powerlifting }}
  \resumeSubHeadingListEnd
  \vspace{-16pt}

    \resumeSubHeadingListStart
      \resumeSubheadingBoldNotBold
      {Gonzaga College High School}{}
      {Grade: Salutatorian}{}
      
      {\small{\textbf{Awards:} 2nd/100+ Nationally in the General Aviation Manufacturers Association Design Challenge, MATHCOUNTS Community Coaching Scholarship National Finalist}}  
  \resumeSubHeadingListEnd
\vspace{-16pt}
% adjust vscape based on the space you want to leave between each section.


  %-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {National Institute of Standards and Technology}{Gaithersburg, Maryland}
      {Guest Researcher}{September 2024 -- Present}
      \resumeItemListStart
        \resumeItem {Continuing mathematical research, using radial basis functions to approximate partial integrodifferential equations to model Biological Field Effect Transistors.}
        \resumeItem {Collaborating with researchers at NIST and developing custom optimization techniques and neural networks in MATLAB and C.}
        \resumeItemListEnd
    \resumeSubSubheading
    {Summer Undergraduate Research Fellow}{June 2024 -- September 2024}
          \resumeItemListStart
                \resumeItem {Conducted math research under mentorship, modeled a biosensor that detects molecular binding with surface potential.}
                \resumeItem{Implemented a neural network to model differential equations using various analytical and numerical methods. Analyzed model convergence in MATLAB.}
                \resumeItem {Compiled data and showcased findings and custom analytical and numerical techniques.}
                \resumeItem {Improved convergence of model from first order to fifth order.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-6pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Multithreaded Mandelbrot Renderer} $|$ \emph{C++, SDL2, Graphical User Interface}}{\ }
          \resumeItemListStart
            \resumeItem{Designed a graphical Mandelbrot Set renderer using the SDL library that utilizes multiprocessing.}
            \resumeItem{Implemented a synchronized queue of functions with atomics and mutexes.}
            \resumeItem{Implemented arbitrary length precision for infinite zoom capabilities.}
          \resumeItemListEnd
          \vspace{-14pt}
        \resumeProjectHeading
          {\textbf{TUI Derivative Calculator} $|$ \emph{Java, Textual User Interface}}{\ }
          \resumeItemListStart
            \resumeItem{Created RPN calculator that calculates and simplifies derivatives of algebraic functions.}
            \resumeItem{Learned programming concepts such as abstract syntax trees and shunting yard algorithm.}
          \resumeItemListEnd
          \vspace{-14pt}
        \resumeProjectHeading
          {\textbf{UNIFIT (Fullstack Website)} $|$ \emph{ReactJS, NodeJS, MongoDB, ExpressJS, Material UI}}{\ }
          \resumeItemListStart
            \resumeItem{Developed a platform for university students to rent, buy, and sell clothes on college campuses}
            \resumeItem{Created forms for making accounts, posting items, and other similar tasks. Created the ability to edit posts, and created a homepage with parallax scrolling images. Implemented user account creation and deletion.}
            \resumeItem{Led website design and security. Protected website against URL injection attacks.}
          \resumeItemListEnd
          \vspace{-3pt}
    \resumeSubHeadingListEnd
\vspace{-3pt}
%-----------Volunteering Experience-----------
\section{Volunteering Experience}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Gonzaga-WJA Science Fair} \hfill { September 2021--February 2023}
     \vspace{-7pt}
    \resumeItemListStart
        \resumeItem{Co-founded, coordinated, and participated in a science fair collaboration with Title-1 middle school where 24 students were paired with high school students.}
        \resumeItem{The collaboration has continued for 4 years and has served 100+ youth since its founding.}
    \resumeItemListEnd
    }}
 \end{itemize}
 \vspace{-16pt}
%-----------Technical Skills-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Programming Languages} {\ }
     \vspace{-7pt}
    \resumeItemListStart
        \resumeItem{\textbf{Proficient:}{ C/C++, MATLAB, Java, Git}}
        \resumeItem{\textbf{Familiar:}{ Python, JavaScript/React, Bash}}
    \resumeItemListEnd

    }}
 \end{itemize}
 \vspace{-3pt}


\vspace{-5.5mm}
 
\end{document}
